library(tidyverse)

---
title: "A UN Report on the Relationship between GDP and Life Expectancy"
author: "Arwen Frick-Cheng"
date: "8/3/2021"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
``` 

```{r load_packages}
library(tidyverse)
```
This report was prepared to the attention of the United Nations. It analyzes the relationship between a country's GDP, its life expectancy and CO2 emissions. Our goal is to determine to what degree a country’s economic strength or weakness may be related to its public health status and impact on climate pollution. We hypothesize that both life expectancy and CO2 emissions increase with a country's GDP.

```{r load_data}

gapminder_1997 <-  read_csv("../data/gapminder_1997.csv")

```

```{r plot_gdp_life_exp}

ggplot(data = gapminder_1997) +
  aes(x = gdpPercap, y = lifeExp, 
      color = continent, size = pop/1e6)+
  labs(x = "GDP Per Capita", y = "Life Expectancy", 
       title = "Do People in Wealthy Countries Live Longer?", 
       size = "Population in Millions")+
  geom_point()+
  scale_color_brewer(palette = "Set1")
```


