library(tidyverse)

---
title: "A UN Report on the Relationship between GDP and Life Expectancy"
author: "Arwen Frick-Cheng"
date: "8/3/2021"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
``` 

```{r load_package, include=FALSE}
library(tidyverse)
```

# Introduction

This report was prepared to the attention of the United Nations. It analyzes the relationship between a country's GDP, its life expectancy and CO2 emissions. Our goal is to determine to what degree a country’s economic strength or weakness may be related to its public health status and impact on climate pollution. We hypothesize that both life expectancy and CO2 emissions increase with a country's GDP.

```{r load_data}

gapminder_1997 <-  read_csv("../data/gapminder_1997.csv")

```
# Results
```{r plot_gdp_life_exp, echo=TRUE}

#echo = true shows the code
#echo = false shows just the output (graph)
#include= TRUE it will show the code AND the output (default)

ggplot(data = gapminder_1997) +
  aes(x = gdpPercap, y = lifeExp, 
      color = continent, size = pop/1e6)+
  labs(x = "GDP Per Capita", y = "Life Expectancy", 
       title = "Do People in Wealthy Countries Live Longer?", 
       size = "Population in Millions")+
  geom_point()+
  scale_color_brewer(palette = "Set1")
```

```{r calculate_summary_statistics, include=FALSE}
ncountries <- gapminder_1997 %>%
  select(country) %>%
  n_distinct()

minGDP <- gapminder_1997 %>%
  summarise(round(min(gdpPercap)))

maxGDP <- gapminder_1997 %>%
  summarise(round(max(gdpPercap)))

```
for this analysis `r ncountries` countries were analyzied for this report. The minimum GDP per capita was `r minGDP`, The minimum GDP per capita was `r maxGDP`, (it will insert in the answers from those variables of the previous code chunk)

below this will insert a table into the report (https://www.tablesgenerator.com/markdown_tables)

| indicator | value   |
| --- | --- |
| minGDP | `r minGDP` |
| MaxGDP | `r maxGDP` |
|   |   |
|   |   |

````{r make_table_with_kable, echo=FALSE}
gapminder_1997 %>%
  filter(continent=="Oceania") %>%
  #specifically pulls the package knitr (not loaded, just referring this specific function)
  #kable makes a table
  knitr::kable()
```

* __R__
* _ggplot_ 
* ___How to analyze RNAseq data___

1. __R__
2. _ggplot_
3. ___How to analyze RNAseq data___
4. [cheatsheet for markdown](https://www.rstudio.com/wp-content/uploads/2015/02/rmarkdown-cheatsheet.pdf) 

